String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-09 2023-1-19/sections/implementation.tex
revise syntax in implementation

We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting into a version of OSTRICH called OSTRICH$^{\rm RECL}$.
Then we do experiments on two benchmark suites, to evaluate the performance of OSTRICH$^{\rm RECL}$.  In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.

>>>>

We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting into\denghang{in} a version of OSTRICH called OSTRICH$^{\rm RECL}$.
Then we do experiments on two benchmark suites, to evaluate the performance of OSTRICH$^{\rm RECL}$. In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.
